\documentclass{practical-resume}
\pagenumbering{arabic} %page numbering

%Custom Variables
\newcommand*{\name}{Rui Sousa} 

% Footer to Direct Readers to Website Resume.
\newcommand{\foot}{Curriculum Vitae - Rui Sousa}

%fonts
\setmainfont{TeX Gyre Termes}
\setsansfont{TeX Gyre Heros}

\usepackage{hyperref}
\hypersetup{
    pdftitle={Aggregate Green Elasticity},
    pdfauthor={Rui Sousa},
    colorlinks=true,
    linkcolor=blue,
    citecolor=magenta,
    filecolor=magenta,      
    urlcolor=magenta,
    pdfpagemode=FullScreen
}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Header
% prints your name
\namehead

% Links
\begin{address}{
	Office 3436, \\
	Kellogg Global Hub, \\
	2211 N Campus Dr, \\
	Evanston, IL 60208 \\
	United States
}
{rui.agm.sousa@u.northwestern.edu}
{https://ruiagmsousa.github.io}
{\today}
\end{address}

\sectionheading{Current Position}
\organization{Northwestern University}{Evanston, IL}{2021-2027 (Exp.)}
\begin{position}{PhD Student, Economics Department}{}
	\item Master of Arts, 2022
\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Work Experience
\sectionheading{Past Employment}

	\organization{London School of Economics}{London, United Kingdom}{Sep 2020 - Sep 2021}
	\begin{position}{Research Assistant - }{Centre For Macroeconomics}
		\item Advisors: Profs. Benjamin Moll \& Ricardo Reis
	\end{position}


	\organization{European Central Bank}{Frankfurt Am Main, Germany}{Jun 2018 - Sep 2021}
	\begin{position}{Analyst, }{Jun 2019 - Sep 2020}
		\item Crisis Management - Quantitative Cluster
	\end{position}
	\begin{position}{Trainee, }{Jun 2018 - Jun 2019}
		\item Stress Test Modelling
	\end{position}
		
\organization{Banco BPI}{Lisbon, Portugal}{Jun 2017 - Aug 2017}
	\begin{position}[noitemize]{Intern, }{Private Banking}
	\end{position}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Working Papers
\sectionheading{Research}
	
	\organization{Working Papers}{}{}
	\begin{itemize}
	\item The Aggregate Green Elasticity of Substitution (\href{https://ruiagmsousa.github.io/research/agg-green-elasticity}{Draft})
		
	\begin{cvabstract}
We introduce a new strategy to estimate the aggregate elasticity of substitution between polluting and non-polluting energy. Exploiting variation in US states' energy mixes, we obtain an elasticity of 0.50 --- significantly lower than prior studies. This challenges the notion that the energy transition can occur without compromising economic growth. A bottom-up model links aggregate to sectoral elasticities, highlighting transportation as a key constraint. Crucially, aggregate elasticity dynamics depend more on micro-level substitution patterns than on the distribution of the energy mix. Consistent with this, we find no evidence of rising substitutability over the past decade despite rapid clean energy adoption.
	\end{cvabstract}

	\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Work in Progress
\organization{Work in Progress}{}{}
	\begin{itemize}
		\item The Distributional Effects of Climate Change
	\end{itemize}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Education 
\sectionheading{Education}

\organization{Nova School of Business and Economics}{Lisbon, Portugal}{2016-2019}
	\begin{position}{MSc Economics}{}
		\item GPA $19/20$ (A)
		\item Exchange Program at Copenhagen University
	\end{position}

\organization{University of Porto}{Porto, Portugal}{2013-2016}
	\begin{position}{BSc Economics}{}
		\item GPA $18/20$ (A)
	\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Teaching
\sectionheading{Teaching}

\organization{Northwestern University}{Evanston, IL}{2022-2024}
	\begin{position}{Teaching Assistant}{}
		\item Intermediate Macroeconomics, Prof. Robert Gordon
		\item International Finance, Prof. Richard Walker
		\item American Economic History since 1865, Prof. Benjamin Chabot
		\item American Economic History before 1865, Prof. Benjamin Chabot
	\end{position}
	
\organization{Nova School of Business and Economics}{Lisbon, Portugal}{2018}
	\begin{position}{Teaching Assistant}{}
		\item Intermediate Macroeconomics, Profs. João Duarte \& Pedro Brinca
	\end{position}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Awars
\sectionheading{Scholarships \& Awards}
\begin{position}{}{}{}
	\item PhD Scholarship, Fundação para a Ciência e a Tecnologia, 2025-2026
	\item Nova SBE Novo Banco Master's Scholarship (\#1), 2016-2019
	\item FEP Belgium Trip Award (top 3 cohort students), 2015
\end{position}
	
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Skills
\sectionheading{Skills}
\vspace{-1em}
	
	\begin{itemize}
		\item Time-series Econometrics
		
		\item Microeconometrics

		\item Dynamic Equilibrium Models	
	
		\item \textbf{Programming Languages:} R, Python, Matlab, SQL
	
		\item \textbf{Languages:} English, Portuguese (Fluent); French, Spanish (Conversational)

	\end{itemize}
		
\end{document}
